Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-20 doc/PRF2022/PRF_main.tex
yny

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 198 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$. (b)-(d) show the equilibrium states for $b=1, 2, 0$, respectively.}
\end{caption}
\end{figure}

@@

\section{Results}
\label{sec:results}
\begin{figure}
\caption{\label{fig:ves_shear} A vesicle in shear flow}
\end{figure}
\begin{figure}
\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
\end{figure}
\subsection{Boundary condition (i):   bilayer configurations}
The vesicle in a shear flow undergoes the familiar tank-treading deformation.
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*$
for vesicles comprised of amphiphilic Janus particles.

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.0655, 0.075\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

@@

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{shear_0.png}
  \includegraphics[width=0.32\textwidth]{shear_1000.png}
  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

>>>>

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

Under background flows, the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit many familiar behaviors of a vesicle \cite{Fu2022_JFM}: 
Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.

In this work we take advantage of the flexibility of the model to examine the effects of boundary condition on JP surfaces that could be controlled based on the chemicals used in the experiments, for example.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}\\
  \includegraphics[width=0.32\textwidth]{Nb198b_eta.pdf}
  \includegraphics[width=0.32\textwidth]{Nb198c_eta.pdf}
  \includegraphics[width=0.32\textwidth]{Nb198d_eta.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 198 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$. (b)-(d) show the equilibrium states for $b=1, 2, 0$, respectively.}
\end{caption}
\end{figure}

@@

\section{Results}
\label{sec:results}

%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in shear flow}
%\end{figure}
%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
%\end{figure}

\subsection{Boundary condition (i):   bilayer configurations}
The vesicle in a shear flow undergoes the familiar tank-treading deformation.
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*$
for vesicles comprised of amphiphilic Janus particles.

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
    \includegraphics[width=0.22\textwidth]{VS_3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.0655, 0.075\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

@@

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{vesTG_0.png}
  \includegraphics[width=0.32\textwidth]{vesTG_2500.png}
  \includegraphics[width=0.32\textwidth]{vesTG_5000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

%
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{shear_0.png}
  \includegraphics[width=0.32\textwidth]{shear_1000.png}
  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}
